DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
small addition

The design of our synthesizer consists of two main phases, an inductive
synthesis phase, {\sc synthesise}, and a validation phase, {\sc verify},
which interact via a finite set of test vectors that is updated
incrementally.  Given a stability and safety specification, the
inductive synthesis procedure tries to find a candidate solution
satisfying the specification for the given set of test inputs.
%
If the synthesis phase succeeds in finding a witness, this witness is
a candidate solution to the full synthesis formula.  We pass this
candidate solution to the validation phase, which checks whether it is
a full solution (i.e., satisfies the specification for all possible
inputs).  If this is the case, then the algorithm terminates.
Otherwise, additional information is provided to the inductive
synthesis phase in the form of a new counterexample that is added to
the set of test inputs, and the loop iterates again.

>>>>

The design of our synthesizer consists of two main phases, an inductive
synthesis phase, {\sc synthesise}, and a validation phase, {\sc verify},
which interact via a finite set of test vectors that is updated
incrementally.  Given a stability and safety specification, the
inductive synthesis procedure tries to find a candidate solution
satisfying the specification for the given set of test inputs.
%
If the synthesis phase succeeds in finding a witness, this witness is
a candidate solution to the full synthesis formula.  We pass this
candidate solution to the validation phase, which checks whether it is
a full solution (i.e., satisfies the specification for all possible
inputs).  If this is the case, then the algorithm terminates.
Otherwise, additional information is provided to the inductive
synthesis phase in the form of a new counterexample, C-ex, that is added to
the set of test inputs, and the loop iterates again.
